Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-04 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: minor corrections

We now consider the cubic EFT of GR.
%
In Fig.~\ref{fig:cEFT_exec_sum} we show the marginalized posterior distributions
functions of $\ell_{\rm cEFT}$ for GW150914 (top panel) and GW200129 (middle panel),
with black (purple) curve corresponding to $N_{\rm max} = 0$ ($N_{\rm max} = 1$) in
the spin expansion.
%
We find that in this theory, the posterior distributions are mostly uniform for
$\ell_{\rm cEFT} \lesssim 40$~km (contrast this with the EdGB and dCS gravity
cases; cf.~Figs.~\ref{fig:edgb_exec_sum} and~\ref{fig:dCS_exec_sum}).
%
For values $\ell_{\rm cEFT} \gtrsim 40$~km, the posteriors smoothly approach zero.

In Fig.~\ref{fig:cEFT_cdf} we show the cumulative distribution functions for
both events, calculated as done in EdGB and dCS cases.
%
We see that curves are very similar to those of dCS gravity for GW200129 (cf.
bottom panel in Fig.~\ref{fig:cEFT_cdf}).
%
We find that for both events both the EFT~\eqref{eq:eft_bound} and ParSpec~\eqref{eq:parspec_bound}
bounds are satisfied for $\mathfrak{m} = M_f$ and $N_{\rm max} = 1/2$, allowing us to obtain the
combined bound from both events
%
\begin{equation}
    \ell_{\rm cEFT} \leqslant 51.3~\textrm{km},
\end{equation}
%
at 90\% credibility. As also happened for our study for dCS, the find that for
the cubic EFT that the ParSpec bound is violated by the $n = 1$ corrections to
the QNMs, implying that we cannot use the associated posterior distributions on
$\ell_{\rm cEFT}$ to draw any meaningful constraint on this parameter.

>>>>

We now consider the cubic EFT of GR.
%
In Fig.~\ref{fig:cEFT_exec_sum} we show the marginalized posterior distributions
functions of $\ell_{\rm cEFT}$ for GW150914 (top panel) and GW200129 (middle panel),
with different curve colors corresponding to different $N_{\rm max}$ in
the spin expansion.
%
We find that in this theory, the posterior distributions are mostly uniform for
$\ell_{\rm cEFT} \lesssim 40$~km (contrast this with the EdGB and dCS gravity
cases; cf.~Figs.~\ref{fig:edgb_exec_sum} and~\ref{fig:dCS_exec_sum}).
%
For values $\ell_{\rm cEFT} \gtrsim 40$~km, the posteriors smoothly approach zero.

In Fig.~\ref{fig:cEFT_cdf} we show the cumulative distribution functions for
both events, calculated as already described for the EdGB and dCS cases.
%
We see that curves are very similar to those of dCS gravity for GW200129 (cf.
bottom panel in Fig.~\ref{fig:cEFT_cdf}).
%
Moreover, we find that for both events both the EFT~\eqref{eq:eft_bound} and
ParSpec~\eqref{eq:parspec_bound} bounds are satisfied for $\mathfrak{m} = M_f$
and $N_{\rm max} = 1/2$, allowing us to obtain the combined bound
%
\begin{equation}
    \ell_{\rm cEFT} \leqslant 51.3~\textrm{km},
\end{equation}
%
at 90\% credibility. As also happened for our study for dCS, the find that for
the cubic EFT that the ParSpec bound is violated by the $n = 1$ corrections to
the QNMs, implying that we cannot use the associated posterior distributions on
$\ell_{\rm cEFT}$ to draw any meaningful constraint on this parameter.
